Flaring star-planet interactions in Kepler and TESS

### 2023-05-19 src/tex/ms.tex
[showyourwork] overleaf sync

% Title
\title{Flaring star-planet interactions in star-planet systems in Kepler and TESS}

@@

Our goal was to measure magnetic star-planet interaction as the presence of excess flares in phase with the innermost planet's orbit. We searched all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively, for flares. For the star-planet systems in the resulting flare catalog~(Section~\ref{sec:results:catalog}), we confirmed that the orbital phase could be known well enough for the entire observing baseline of the system~(Section~\ref{sec:results:coherence}). Knowing that, we could calculate the orbital phases of each flare, and the flare phase distributions for each system~(Section \ref{sec:results:phasedist}). We then applied the custom Anderson-Darling test to check how much each distribution was different from randomly distributed intrinsic flaring. Comparing the test results with the expected power of magnetic star-planet interaction, we found that the amount of excess flaring tentatively increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}). However, not all systems with high expected power show signs of flaring SPI, which appears as a branching in the distribution of test results. To prepare the subsequent discussion, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude some systems from the analysis in Section~\ref{sec:results:individualstars}.
\subsection{Flare catalog}
\label{sec:results:catalog}
We searched a total of 3032 Kepler Quarters and 4181 TESS Sectors of a total of 1811 star-planet systems for flares. We inspected all candidates manually, and added flares observed by K2 on TRAPPIST-1~\cite{paudel2018k2}, and flares from the planet hosting primary in the Kepler-411 binary~\cite{jackman2021stellara}. The final table contains a total of \input{output/PAPER_total_number_of_flares.txt} flares in \input{output/PAPER_total_number_of_systems_with_flares.txt} systems. In Table~\ref{tab:flares}, we list all the flares and their characteristics. To identify each event, we provide the name of the system in which the flare was found, along with its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively. For each flare, we also give the start and finish time, relative amplitude $a$ and equivalent duration $ED$. If the transit midtime is known for the innermost planet, we also give the orbital phase at which the flare occurred. The full table is provided with the supplementary material, and via Zenodo (see Data Availability Statement).

@@

\subsection{Period coherence times}
\label{sec:results:coherence}
In many cases, the observing baseline covered by Kepler and TESS for a given system can span multiple years. In these cases, the orbital period of the innermost planet must be known very precisely so that we can assign accurate orbital phases to the flare events.
We test this by dividing the timespan between the first and the last flare in the combined Kepler and TESS observations by the coherence time $\tau$ of the orbital period for each system. We calculate the coherence time as

\begin{equation}
    \tau = P^2 / \sigma_P,
\end{equation}
where $P$ is the orbital period, and $\sigma_P$ is its uncertainty.
If the orbital period is well-known, the resulting ratio should be $<<1$. The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of these ratios in our sample. The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of last flare is at most $2\%$ off, compared to the first. The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively. We keep these systems in our sample, but caution that the measured absence of flaring SPI might be due to the uncertain orbital period of the planet in these cases.

We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel). There are three reasons for this: First, the uncertainty for the rotation was not always provided, in which case we assigned a $10\%$ error. Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and/or rapidly evolving. And third, differential rotation causes spots at different latitudes to move at different speeds, so it becomes difficult to even define a rotation period, as long as we don't know at which latitude(s) the flares occur~(see also Section~\ref{sec:discussion:rotsyn}).

@@

\subsection{Flare phase distributions}
\label{sec:results:phasedist}
Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and return the significance of the deviation between the two. In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[e.g.][]{doyle2018investigating,howard2021evryflare}. Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively. The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve.

@@

\subsection{Flaring star-planet interaction signal}
\label{sec:results:spi}
We used the custom Anderson-Darling test introduced in~\citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations. We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares. In~\citet{ilin2022}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below. It is also the only star in our sample, for which the threshold makes a difference in the significance of the Anderson-Darling test. However, we note that we lose four systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, and Kepler-1084. The flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.

Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system. There is no star-planet system for which we find a $>3\sigma$ signal of star-planet interaction in our sample. However, overall, the significance of the deviation increases with higher expected power of interaction, which is also listed for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.

Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches on the high end of expected powers. On one branch, the significance of the measured interaction is correlated with the expected power $P$. On the other branch, no interaction is measured regardless of the expected power $P$.

@@

\subsection{Individual stars}
\label{sec:results:individualstars}
The properties of star-planet systems in this work are diverse, including both very young and old systems (with slowly rotating host stars); systems with super-Earths, Neptunes, and Hot Jupiters; and spectral types covering the lower main sequence from early G to late M dwarfs.

For our analysis, it is important to know that the observed flares indeed occurred on the planet host star. We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}). One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but was excluded for other reasons~(Section~\ref{sec:results:individualstars:kep411}). We also dropped GJ 1061 from the sample because its rotation period was unconstrained. Another uncertainty in our analysis is the possibility of additional planets at even shorter orbits than the currently known innermost planet, such as might be the case for Proxima Cen~(Section~\ref{sec:results:individualstars:proxima}).

The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring that could be indicative of flaring star-planet interaction. In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}). Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP 26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
\subsubsection{Excluded targets}
\label{sec:results:individualstars:excluded}

While they appear in Table~\ref{tab:flares}, we excluded a number of systems from further analysis. We drop all multiple stars except for Proxima Cen (whose components are well separated both physically, and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from Gaia DR2 and ground-based adaptive optics~\citep{ziegler2018measuring}: \input{output/multiples_string.tex}.

For instance, Kepler-808 (KOI 1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\citep{baranec2016roboao}. TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate come from both stars~\citep{bouma2020cluster}. HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total flux.

@@

\subsubsection{Kepler-411}
\label{sec:results:individualstars:kep411}
Kepler-411 has a 3 mag fainter companion~\citep{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis initially. The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare. \citet{jackman2021stellara} disentangle the contributions from each component on a pixel level. According to \citet{morton2016false, sun2019kepler411}, Kepler-411's planets orbit the primary companion. The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7. Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $ED<1\,$s, which excludes Kepler-411 from further analysis.

\subsubsection{Proxima Cen}
\label{sec:results:individualstars:proxima}
We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{kavanagh2021planetinduced}. However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction. The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions. However, the orbital period of the tentative planet is so uncertain at this point that its coherence time is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.

@@

K2-25 is a multiplanet system around a fast rotating ($P_{rot}<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}. This might in part be due to the stellar wind conditions around K2-25 b. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).

@@

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(top row in Figure~\ref{fig:adtest_bp}). In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring. In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit. It is important to note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained. All else equal, this is more likely if the stellar magnetic field strength is weaker. Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two Sections.

\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2\sigma$ level, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.61$ and $\sim 0.81$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.

HIP 67522 is a young Sun, currently contracting onto the main sequence. It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}. Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{\rm orb}=5/1$. Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet. However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.

@@

\section{Discussion}
\label{sec:discussion}
Eccentricity is almost controlled for in our sample~(Section~\ref{sec:discussion:eccentricity}), while rotation is not well enough constrained to investigate the presence of flaring modulation with $P_{rot}$, or the synodic period~(Section~\ref{sec:discussion:rotsyn}). In the remainder of the discussion, we lay out different reasons for the emerging shape of the distribution in our results in Fig.~\ref{fig:adtest_bp}, in particular the inactive and active branches at high expected power of interaction. We begin with the possible intermittency of the interaction that could be caused by the planet regularly moving in and out of the sub-Alfv\'enic zone for extended periods of time~(Section~\ref{sec:discussion:intermittency}). In Section~\ref{sec:discussion:viewing}, we suggest that the absence of interaction at high expected power could be due to unfavorable viewing geometry of the system, e.g., a face-on orbital plane. In Section~\ref{sec:discussion:commensurability}, we note that systems on the inactive branch are further away from spin-orbit commensurability than stars on the active branch. This leads us to conjecture a possible link between spin-orbit resonance and flaring SPI.

\subsection{Eccentricity}
\label{sec:discussion:eccentricity}
If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius. If then the apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage. This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}. In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$. The exception is K2-25, with a relatively high $e=0.45$. If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further increased by the narrow phase range of the periastron passage. \citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}). We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity.

\subsection{Rotational and synodic variability}
\label{sec:discussion:rotsyn}
Our analysis is the most comprehensive search for flaring star-planet interactions to date, using the full Kepler and most recent TESS archives of light curves. We considered exploiting it beyond the search for variations with orbital period, and additionally look for variability with rotation period, and synodic period. Here, we explain why we ultimately decided not to do so.

>>>>

% Title
\title{Flaring star-planet interactions in Kepler and TESS}

@@

Our goal was to measure magnetic star-planet interaction as the statistical clustering of flares in phase with the innermost planet's orbit. We searched all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively, for flares. For the star-planet systems in the resulting flare catalog~(Section~\ref{sec:results:catalog}), we confirmed that the orbital phase could be known well enough for the entire observing baseline of the system~(Section~\ref{sec:results:coherence}). We calculated the orbital phases of each flare, and the flare phase distributions for each system~(Section \ref{sec:results:phasedist}). We then applied the custom Anderson-Darling test to assess how much each distribution was different from randomly distributed intrinsic flaring. Comparing the test results with the expected power of magnetic star-planet interaction, we found that the amount of excess flaring tentatively increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}). However, not all systems with high expected power show signs of flaring SPI, which creates two branches in the distribution of test results. Finally, in Section~\ref{sec:results:individualstars}, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude others from the analysis.

\subsection{Flare catalog}
\label{sec:results:catalog}
We searched a total of 3032 Kepler Quarters and 4181 TESS Sectors of a total of 1811 star-planet systems for flares. We inspected all candidates manually, and added flares observed by K2 on TRAPPIST-1~\citep{paudel2018k2}, and flares from the planet hosting primary in the Kepler-411 binary~\citep{jackman2021stellara}. The final table contains a total of \input{output/PAPER_total_number_of_flares.txt}flares in \input{output/PAPER_total_number_of_systems_with_flares.txt}systems. In Table~\ref{tab:flares}, we list the flares and their characteristics. To identify each event, we provide the name of the system in which the flare was found, along with its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively. For each flare, we also give the start and finish time, relative amplitude $a$ and equivalent duration $ED$. If the transit midtime is known for the innermost planet, we also give the orbital phase at which the flare occurred. The full table is provided with the supplementary material, and via Zenodo (see Data Availability Statement).

@@

\subsection{Period coherence times}
\label{sec:results:coherence}
In many cases, the observing baseline covered by Kepler and TESS for a given system can span multiple years. In these cases, the orbital period of the innermost planet must be known very precisely so that we can assign accurate orbital phases to the flare events.
We test this by dividing the timespan $\Delta T$ between the first and the last flare in the combined Kepler and TESS observations by the coherence time $\tau$ of the orbital period for each system. We calculate the coherence time as

\begin{equation}
    \tau = P^2 / \sigma_P,
\end{equation}
where $P$ is the orbital period, and $\sigma_P$ is its uncertainty.
If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $<<1$. The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample. The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of the last flare is at most $2\%$ off, compared to the first. The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively. We keep these systems in our sample, but caution that the measured absence of flaring SPI might be due to the uncertain orbital period of the planet in these cases.

We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel), so that a statistical analysis of rotational flare modulation is not feasible.

\citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per that period. However, the uncertainty in $P_{\rm rot}$ does not allow us to search for modulation with synodic period. We argue, however, that in a transiting system with high orbital inclination, the effect with synodic period reduces to modulation with the orbital period:

If the orbital axis inclination is high, then the passage will regularly occur on the back of the star relative to the observer. The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal. As a consequence, to detect a modulation with the synodic period, a significantly longer observing baseline is needed than to detect a modulation with the orbital period. Additionally, if there are many active regions (at the same time, or in sequence) that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period further converges to a modulation with orbital period. 
In our sample, the observing baseline is multiple years long for many systems. Most stars, even the most rigidly rotating late M dwarfs, show variability in their spot modulation on such long timescales~\citep[e.g.,][]{giles2017kepler,davenport2015spots, namekata2019lifetimes}).

% Even if differential rotation was absent and active regions were extremely stable, we would likely be unable to observe the passage of the sub-planetary point over the flare-prone region every synodic period.

%However, this assumes that the landscape of active regions on the star is stable throughout the entire observing time, and that the number of such regions in the footpoint passageway is low enough to produce a periodic modulation. Note that this is a different effect from the geometrical modulation of visibility we look for in modulation with the orbital period in this study.

%Even for the few stars, for which the rotational period is known precisely enough, we need to make numerous assumptions. These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface. For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase.

%There are three reasons for this: First, the uncertainty for the rotation was not always provided, in which case we assigned a $10\%$ error. Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and/or rapidly evolving. And third, differential rotation causes spots at different latitudes to move at different speeds, so it becomes difficult to even define a rotation period, as long as we don't know at which latitude(s) the flares occur~(see also Section~\ref{sec:discussion:rotsyn}).

@@

\subsection{Flare phase distributions}
\label{sec:results:phasedist}
Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and returns the significance of the deviation between the two. In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[see, e.g.,][]{doyle2018investigating,howard2021evryflare}. Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively. The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve, which arise due to varying noise levels between individual Quarter/Sectors, and Kepler and TESS.

@@

\subsection{Flaring star-planet interaction signal}
\label{sec:results:spi}
We used the custom Anderson-Darling test introduced in Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations. We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares. In~\citet{ilin2022searching}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below. It is also the only star in our sample, for which this threshold makes a difference in the significance of the Anderson-Darling test. However, we note that we lose four systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, and Kepler-1084. We note that the flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.

Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system. There is no star-planet system for which we find a $>3\sigma$ signal of star-planet interaction in our sample. However, overall, the significance of the deviation increases with higher expected power $P_{xx}$ of interaction, where the subscript denotes different scenarios  introduced in Section~\ref{sec:methods:pspi}. Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.

Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches on the high end of expected powers. On one branch, the significance of the measured interaction is correlated with the expected power $P_{xx}$. On the other branch, no interaction is measured regardless of the expected power $P_{xx}$.

@@

\subsection{Individual stars}
\label{sec:results:individualstars}
The properties of star-planet systems in this work are diverse, including both very fast and very slowly rotating host stars; systems with super-Earths, Neptunes, and Hot Jupiters; and spectral types covering the lower main sequence from mid-F to late M.

For our analysis, it is important to know that the observed flares indeed occurred on the planet host star. We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}). One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded for other reasons~(Section~\ref{sec:results:individualstars:kep411}). We also dropped GJ 1061 from the sample because its rotation period was unconstrained. Another uncertainty in our analysis is the possibility of additional planets at even shorter orbits than the currently known innermost planet, such as might be the case for Proxima Cen~(Section~\ref{sec:results:individualstars:proxima}).

The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring. In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P_{xx}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}). Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP~26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
\subsubsection{Excluded targets}
\label{sec:results:individualstars:excluded}

While they appear in the flare catalog~(Table~\ref{tab:flares}), we excluded a number of systems from further analysis. We drop all multiple stars except for Proxima Cen (whose components are well separated both physically, and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from Gaia DR2 and ground-based adaptive optics~\citep{ziegler2018measuring}: \input{output/multiples_string.tex}

For instance, Kepler-808 (KOI-1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\citep{baranec2016roboao}. TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate come from both stars~\citep{bouma2020cluster}. HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total flux.

@@

\subsubsection{Kepler-411}
\label{sec:results:individualstars:kep411}
Kepler-411 has a 3 mag fainter companion~\citep{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis initially. The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare. \citet{jackman2021stellara} disentangle the contributions from each component on a pixel level. According to \citet{morton2016false, sun2019kepler411}, Kepler-411's planets orbit the primary companion. The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7. Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $ED<1\,$s, which excludes Kepler-411 from further analysis. Note that we do not find the low energy flares to cluster in orbital phase, either.

\subsubsection{Proxima Cen}
\label{sec:results:individualstars:proxima}
We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{kavanagh2021planetinduced}. However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction. The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions. However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.

@@

K2-25 is a multiplanet system around a fast rotating ($P_{\rm rot}<2\,$d) mid-M dwarf in the Hyades open cluster~\citep[600-800 Myr, ][]{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}. This might in part be due to the stellar wind conditions around K2-25 b. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).

@@

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(top row in Figure~\ref{fig:adtest_bp}). In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear. In both cases, the low level (or possible absence) of interaction could be due to the Alfv\'en radius being within the planetary orbit. It is important to note that the scaling laws introduced in Section~\ref{sec:methods:pspi} assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained. All else equal, a planet is more likely sub-Alfv\'enic if the stellar magnetic field is strong. Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two Sections.

\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2\sigma$ level, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.61$ and $\sim 0.81$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, within 10 hours after mid-transit.

HIP 67522 is a young Sun, currently contracting onto the main sequence. It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}. Curiously, the planet is in close spin-orbit commensurability -- $P_{\rm rot}/P_{\rm orb}\approx 1/5$. Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet. However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period. So we cannot rule out rotational modulation yet, although the clustering close to transit is suggestive.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.

@@

\section{Discussion}
\label{sec:discussion}

Our results in Fig.~\ref{fig:adtest_bp} are tentative, yet the trend between expected power of interaction and measured clustering of flares in orbital phase is suggestive, as is the appearance of an active and an inactive branch at high expected powers. We can now consider additional facts about the systems, as well as processes, that may explain the observed trends. Beyond the extent of the Alfv\'en radius that decides over the possibility of magnetic interaction in the first place~(Section~\ref{sec:intro:mspi}), orbital eccentricity can further enhance magnetic SPI signal, but is low for most systems in our sample except for K2-25~(Section~\ref{sec:discussion:eccentricity}). The observed branching might also be explained by intermittent SPI~(Section~\ref{sec:discussion:intermittency}), but its possible causes are not well known. As an easier to test alternative explanation, we highlight the important influence of viewing geometry on the observability of flaring SPI, which might explain the absence of magnetic SPI in TAP~26~(Section~\ref{sec:discussion:viewing}).

Magnetic and tidal SPI are difficult to disentangle by their global effects on stellar activity indicators~(Section~\ref{sec:intro:global}). Locally, however, we can discriminate between the two by their relevant periods, that is, $P_{\rm orb}$ and $P_{\rm orb /2}$. In Section~\ref{sec:discussion:tidal}, we repeat the analysis in this paper with $P_{orb}/2$, and find yet more tentative trends in line with scaling laws for tidal interaction. In a system-by-system comparison, we find consistency with the expectation that slowly rotating, likely old, systems can only show local tidal interaction, while rapidly rotating systems with strong magnetic fields can experience both.

\subsection{Eccentricity}
\label{sec:discussion:eccentricity}
Orbital eccentricity can affect magnetic SPI by modulating the planet's distance to the star. If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius. If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage. This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}. In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$. The exception is K2-25, with a relatively high $e=0.45$. If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint is further increased by the narrow phase range of the periastron passage. \citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}). We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity. Statistically, we are more likely to observe a planetary transit close to periastron, since periastron permits more orbital inclinations than apoastron. So, overall, we expect eccentric transiting systems to experience elevated SPI signal.

% \subsection{Rotational and synodic variability}
% \label{sec:discussion:rotsyn}
% Our analysis is the most comprehensive search for flaring star-planet interactions to date, using the full Kepler and most recent TESS archives of light curves. We considered exploiting it beyond the search for variations with orbital period, and additionally look for variability with rotation period, and synodic period. Here, we explain why we ultimately decided not to do so.
